%-------------------------------------------------------------------------------
%	autoCV template (MIT License, Jitin Nair)
%	Adapted for Iuliia Golovchanskaia
%-------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\bfseries\scshape\raggedright\color{darkgray}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\usepackage{fontawesome5}
\usepackage{etoolbox}
\newbool{CVContactPublic}
\newbool{CVAchievementsPublic}

\input{cv-contact-public}
\InputIfFileExists{cv-contact.local.tex}{\input{cv-contact.local.tex}}{}

\input{cv-achievements-public}
\InputIfFileExists{cv-achievements.local.tex}{\input{cv-achievements.local.tex}}{}

%----------------------------------------------------------------------------------------
%	COMPACT LIST
%----------------------------------------------------------------------------------------
\newlist{joblist}{itemize}{1}
\setlist[joblist]{nosep, leftmargin=1.2em, itemsep=2pt, label=\textbullet}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Iuliia Golovchanskaia} \\[5pt]
\large{\textbf{Senior C++ Developer}} \\[7.5pt]
\ifboolexpr{ test {\ifdefempty{\CVEmail}} and test {\ifdefempty{\CVPhone}} }{
\raisebox{-0.05\height}\faEnvelope\ {\small\color{gray}\CVStubEmailDisplay} \ $|$\ \raisebox{-0.05\height}\faMobile\ {\small\color{gray}\CVStubPhoneDisplay}%
}{
\ifdefempty{\CVEmail}{}{%
\href{mailto:\CVEmail}{\raisebox{-0.05\height}\faEnvelope\ \CVEmail}%
}%
\ifdefempty{\CVPhone}{}{%
\ifdefempty{\CVEmail}{}{ \ $|$\ }%
\raisebox{-0.05\height}\faMobile\ \CVPhone%
}%
}%
\ \ $|$\ \raisebox{-0.05\height}\faGlobe\ Cyprus \\[3pt]
\href{https://www.linkedin.com/in/iuliia-golovchanskaia}{\raisebox{-0.05\height}\faLinkedin\ iuliia-golovchanskaia} \ $|$ \
\href{https://github.com/golju}{\raisebox{-0.05\height}\faGithub\ golju}%
\ \ $|$\ %
\ifdefempty{\CVTelegram}{%
\raisebox{-0.05\height}\faTelegram\ {\small\color{gray}\CVStubTelegramDisplay}%
}{%
\href{https://t.me/\CVTelegram}{\raisebox{-0.05\height}\faTelegram\ \CVTelegram}%
} \\
\end{tabularx}

\ifboolexpr{ test {\ifbool{CVContactPublic}} or test {\ifbool{CVAchievementsPublic}} }{
\begin{center}
{\small\itshape\color{darkgray}
Public repository version: NDA-sensitive achievements and direct contact details are omitted. A complete CV is available on request.}
\end{center}
\vspace{2pt}
}{}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
8 years of experience in game development and computer vision. Owns game event features end-to-end at Playrix (Fishdom, 545M+ downloads, 15M MAU). Covers full cycle from architecture design to live-ops delivery. Drives engineering quality and AI-assisted development practices.

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{C++ (17/20)} & STL, RAII, move semantics, design patterns \\
\textbf{Performance} & Multithreading (std::thread, POSIX Threads, CUDA), SIMD (NEON, SSE), profiling (Tracy), neural network inference optimization \\
\textbf{Testing} & Unit testing (Google Test) \\
\textbf{Tools \& Platforms} & Git, bash, CI/CD (TeamCity), macOS, Linux, Windows, Qt, CMake \\
\textbf{AI \& Tooling} & AI-assisted development (Cursor), building internal AI agents, Developer Enablement \\
\textbf{Domains} & Mobile GameDev, classical computer vision (OpenCV), real-time systems \\
\textbf{Engineering Practices} & Design Reviews, Code Review, Agile/Scrum, task decomposition, mentoring \& teaching \\
\textbf{Other Languages} & Python \\
\textbf{English} & Upper-Intermediate (B2) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience (8 Years)}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Playrix $|$ Lead Programmer} & 01.2022 -- Present \\
\small Promoted from Programmer (2023) & \small \textbf{Fishdom} --- match-3 mobile game, 545M+ downloads, 15M MAU \\
\end{tabularx}

\smallskip\noindent\textit{Responsibilities:}
\begin{joblist}
\item Owned architecture and end-to-end implementation of complex game event systems: state machine-driven lifecycle, progression and reward logic, analytics pipelines, and live-ops content delivery.
\item Drove AI-assisted development (Cursor) into engineering workflows, building internal AI agents that improved engineering speed and code quality across feature teams.
\item Established engineering standards: design reviews, code review processes, delivery quality gates, and developer performance evaluation guidelines.
\end{joblist}

\smallskip\noindent\textit{Achievements:}
\begin{joblist}
\item \PlayrixAchOne
\item \PlayrixAchTwo
\item \PlayrixAchThree
\end{joblist}

\medskip\begin{center}\color{gray}\rule{0.3\linewidth}{0.3pt}\end{center}\vspace{-2pt}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Higher School of Economics $|$ C++ Instructor, Saint Petersburg} & 09.2021 -- 11.2022 \\
\end{tabularx}
\vspace{-2pt}
Taught undergraduate students the fundamentals of C++ programming, including algorithms, data structures, and software development best practices.

\medskip\begin{center}\color{gray}\rule{0.3\linewidth}{0.3pt}\end{center}\vspace{-2pt}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Computer Vision Systems $|$ Software Engineer, Saint Petersburg} & 06.2020 -- 12.2021 \\
\small Outsource company delivering computer vision solutions for enterprise clients (oil industry, Huawei) & \\
\end{tabularx}

\smallskip\noindent\textit{Responsibilities:} Developed software for industrial computer vision systems (quality control automation) and urban 3D reconstruction, including city-scale modeling, performance optimization, and service-level communication.

\smallskip\noindent\textit{Achievements:}
\begin{joblist}
\item Designed and integrated RPC-based service communication (rpclib), enabling real-time data exchange between distributed system components.
\item Refactored core computation libraries, achieving a 53\% performance improvement.
\item Built camera management desktop tools (Qt) used by field engineers for calibration and monitoring.
\end{joblist}

\medskip\begin{center}\color{gray}\rule{0.3\linewidth}{0.3pt}\end{center}\vspace{-2pt}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Simicon $|$ Software Engineer, Saint Petersburg} & 08.2018 -- 06.2020 \\
\small Traffic camera systems for road safety and automated violation detection & \\
\end{tabularx}

\smallskip\noindent\textit{Responsibilities:} Developed software components focused on real-time data processing, computer vision, and neural network integration.

\smallskip\noindent\textit{Achievements:}
\begin{joblist}
\item Built data management desktop tools (Qt, PyQt) for operators working with traffic camera systems.
\item Accelerated neural network inference 8x through vectorization (NEON, CUDA), enabling real-time processing on edge devices.
\item Integrated neural networks into production software using CUDA and POSIX Threads for parallel execution.
\item Developed computer vision algorithms for automated traffic violation detection and road situation analysis.
\end{joblist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}X r@{}}
Master's degree, Software Engineering --- \textbf{ITMO University} & 2022 \\[3pt]
Bachelor's degree, Applied Mathematics and Computer Science --- \textbf{Saint Petersburg State University} & 2019 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{AI-Assisted Programming} --- \textbf{NEBIUS} & 2025 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLIC SPEAKING
%----------------------------------------------------------------------------------------
\section{Public Speaking}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Invited Expert & C++ Russia (2020, 2022), PiterPy \\
Host & C++ Russia (2020--2023), YaTalks 2023, C++ Zero Cost Serbia 2023 \\
Speaker & PyLadies Meetup: 3D Scene Reconstruction using OpenCV \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Scientific Publications}
\begin{itemize}[leftmargin=1.2em, itemsep=5pt, label=\textbullet]
\item Building a mixed reality system free from visual discomfort, Proc.\ SPIE 11876, 12.9.2021 \\
\href{https://doi.org/10.1117/12.2597182}{\underline{doi.org/10.1117/12.2597182}}
\item Real-time tracking of surrounding objects in augmented and mixed reality applications, Proc.\ SPIE 11897, 9.10.2021 \\
\href{https://doi.org/10.1117/12.2604208}{\underline{doi.org/10.1117/12.2604208}}
\end{itemize}

\end{document}
